%-------------------------
% Resume in LaTeX
% Author : Branavan Kuganesan
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.25in}

\urlstyle{same}
\raggedright
\setlength{\tabcolsep}{0in}
\setlist[itemize]{leftmargin=1.2em, itemsep=1.5pt, topsep=3pt}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{6pt}

\newcommand{\resumeSubheading}[4]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
  \end{tabular*}\vspace{-4pt}
}

\begin{document}

\begin{center}
  {\Huge \textbf{Branavan Kuganesan}} \\[6pt]
  \faPhone\ +94 724 200 700 \quad
  \faEnvelope\ \href{mailto:branavan09@gmail.com}{branavan09@gmail.com} \quad
  \faGithub\ \href{https://github.com/Branavan2004}{github.com/Branavan2004} \quad
  \faLinkedin\ \href{https://linkedin.com/in/branavan-kuganesan}{linkedin.com/in/branavan-kuganesan} \\[4pt]
  Colombo, Sri Lanka
\end{center}

\section{Professional Summary}
Computer Science undergraduate at the Informatics Institute of Technology (affiliated with the University of Westminster) with hands-on experience building web applications and software projects using Python, JavaScript, Java, React, and SQL. Strong interest in software engineering, problem solving, and data-driven systems, with leadership experience through IEEE student initiatives, event operations, and student representation. Seeking an internship opportunity to contribute to real-world software projects while continuing to strengthen engineering and collaboration skills.

\section{Education}
\resumeSubheading
  {University of Westminster (via IIT Campus)}{2024 -- 2028}
  {BSc (Hons) Computer Science}{Colombo, Sri Lanka}
\textbf{Relevant Modules:} Software Development, Object Oriented Programming, Database Systems, Algorithms and Data Structures, Client Server Architectures, Machine Learning and Data Mining

\vspace{4pt}
\resumeSubheading
  {Royal College Colombo}{2010 -- 2023}
  {Primary and Secondary Education}{Colombo, Sri Lanka}

\section{Projects}
\resumeProjectHeading{F1 2025 Race Simulation}{React, Recharts, SVG, Ergast API}
\begin{itemize}
  \item Built an interactive Formula 1 race simulation platform with real-time race visualization and performance analytics.
  \item Implemented dynamic track rendering and chart-based race insights using SVG graphics and frontend data visualization tools.
\end{itemize}

\resumeProjectHeading{F1 Race Result Calculator}{Python, JavaScript}
\begin{itemize}
  \item Developed a tool to calculate race results, including lap times, penalties, and final standings.
  \item Automated leaderboard generation to improve accuracy and reduce manual result processing.
\end{itemize}

\resumeProjectHeading{Eco Pulse Web Platform}{HTML, CSS, JavaScript}
\begin{itemize}
  \item Created a climate awareness platform aligned with the UN Sustainable Development Goals.
  \item Added volunteer registration features and educational resources to support environmental awareness initiatives.
\end{itemize}

\section{Technical Skills}
\textbf{Languages:} Python, Java, JavaScript, SQL \\
\textbf{Frameworks and Tools:} React, Node.js, Git, GitHub, Docker, Tailwind CSS \\
\textbf{Concepts:} Object Oriented Programming, Data Structures, REST APIs, Software Development Lifecycle \\
\textbf{Professional Skills:} Problem Solving, Team Collaboration, Technical Communication

\section{Experience}
\resumeSubheading
  {St Mary's College, Avissawella}{2024 -- Present}
  {Volunteer Mathematics Teacher}{Avissawella, Sri Lanka}
\begin{itemize}
  \item Conduct mathematics sessions for Grade 11 students with a focus on exam preparation and concept clarity.
  \item Prepare lesson plans and provide one-on-one mentoring tailored to student learning needs.
  \item Help students strengthen analytical thinking and problem-solving skills through guided practice.
\end{itemize}

\section{Leadership and Volunteer Experience}
\resumeSubheading
  {IEEE Student Branch of IIT}{2026 -- Present}
  {Industry Relations Lead}{Colombo, Sri Lanka}
\begin{itemize}
  \item Lead outreach initiatives and industry partnerships that connect students with technology professionals and organizations.
  \item Coordinate technical workshops, networking sessions, and large-scale IEEE events hosted by the student branch.
  \item Manage communication with sponsors, guest speakers, and organizing committees to support smooth event delivery.
\end{itemize}

\resumeSubheading
  {IX'25 and CodeSprint 11}{2025}
  {Industry Outreach Vice Chair}{Colombo, Sri Lanka}
\begin{itemize}
  \item Supported industry engagement programs and networking opportunities for students participating in flagship events.
  \item Assisted with partnership coordination and communication with technology companies and professionals.
\end{itemize}

\resumeSubheading
  {IEEE Student Branch of IIT}{2025 -- Present}
  {IEEE Event Volunteer}{Colombo, Sri Lanka}
\begin{itemize}
  \item Contributed to the organization of IEEE flagship events including \href{https://ieeeiit.org}{CodeSprint X}, AfterMath'25, HackSphere, MicroMaze 2.0, Traction, and RobotNexus.
  \item Supported logistics, participant coordination, and on-ground event operations to ensure smooth execution.
  \item Collaborated with multidisciplinary student teams to deliver technical competitions, workshops, and community initiatives.
\end{itemize}

\resumeSubheading
  {Informatics Institute of Technology}{2024 -- 2026}
  {Batch Representative}{Colombo, Sri Lanka}
\begin{itemize}
  \item Represented the student batch in academic and administrative discussions.
  \item Facilitated communication between students and faculty and supported academic coordination.
\end{itemize}

\section{Certifications}
Docker Foundations Professional Certificate -- Docker \\
React Essential Training -- LinkedIn Learning \\
Learning Python -- LinkedIn Learning

\section{Honors and Awards}
Best Logistics Volunteer -- IEEE Student Branch of IIT \hfill 2025 -- 2026 \\
Best Performer -- International Space Science Competition (Go4Guru)

\section{Languages}
Tamil -- Native \\
English -- Full Professional Proficiency \\
Sinhala -- Professional Working Proficiency

\section{References}
\begin{itemize}
  \item \textbf{Dhanushka Surendra Rathnayake}, Senior Lecturer, Informatics Institute of Technology, Colombo \\
  Email: \href{mailto:dhanushka.d@iit.ac.lk}{dhanushka.d@iit.ac.lk} \quad Phone: +94 77 228 7083
  \item \textbf{Partheepan Radhakrishnan}, Senior Quality Assurance Analyst, LSEG Sri Lanka \\
  Email: \href{mailto:partheepan17@gmail.com}{partheepan17@gmail.com} \quad Phone: +94 77 723 1145
\end{itemize}

\end{document}
